---
title: "R Notebook"
output: html_notebook
---
```{r Libraries}
library(tidyverse)
theme_set(theme_minimal())
```
```{r Getting Data}
artists <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-09-27/artists.csv')
```
# Okay, what are we looking at? 
We have three categorical variables -- `r length(unique(artists$state)) ` states, `r length(unique(artists$race)) ` races, and `r length(unique(artists$type)) ` types of artist. In theory these produce `r length(unique(artists$state)) * length(unique(artists$race)) * 
length(unique(artists$type))` possible combinations, which is the number of observations in the data. 
Not all of these observations, though have all the data. Some have an NA in the `artists_n` and thus the share and quotient -- `r as.numeric(count(artists %>% filter(is.na(artists_n))))`, specifically. Another `r as.numeric(count(artists %>% filter(artists_n == 0)))` have a known number of artists, but it is 0. In the majority of these cases this means that the share and quotient are thus NA, expect for two oddities: 
```{r}
artists %>% filter(artists_n == 0 & !is.na(artists_share))
```
I think it makes sense to: 

1. Remove entries that we just don't have artists counts for 
```{r}
artists <- artists %>% filter(!is.na(artists_n))
```

2. Replace NAs in share and quotient on entries with 0 artists with 0 
Since we know what we have (0 artists) its fair to represent the share as 0 (0/all_workers_n), and we know the quotient must be 100% below the national labor force share. 
```{r}
artists <- artists %>% mutate(artists_share = if_else(artists_n == 0,0, artists_share),location_quotient = if_else(artists_n == 0,0, location_quotient))
```
# Playing with plotting
```{r}
ggplot(artists, aes(all_workers_n, artists_n, color=race)) + geom_point() + geom_smooth()
```
Makes since this doesn't work, numbers would be different. 
```{r fig.width=10, fig.height=4}
ggplot(artists, aes(all_workers_n, artists_n, color=type))  + stat_smooth(geom='line', alpha=0.5, se=FALSE) +  geom_point() + facet_wrap(vars(race), scales="free")
```
Nice! Let's remake some orderings. 
```{r}
race_sort <- (artists %>% group_by(race) %>% summarize(a= mean(all_workers_n,na.rm=TRUE)) %>% arrange(-a))$race
type_sort <- (artists %>% group_by(type) %>% summarize(a= mean(artists_share,na.rm=TRUE)) %>% arrange(-a))$type
artists$race <- factor(artists$race,levels=race_sort,ordered=TRUE)
artists$type <- factor(artists$type,levels=type_sort,ordered=TRUE)
```
```{r fig.width=10, fig.height=4}
ggplot(artists, aes(all_workers_n, artists_n, color=type))  + stat_smooth(geom='line', alpha=0.5, se=FALSE) +  geom_point() + facet_wrap(vars(race), scales="free")
```

